Study of Illumination Dependency in the Dynamic Laser Speckle Analysis

### 2019-08-02 article/article_1.tex
revisado

\title{Analysis of Illumination Dependency  in the Dynamic Laser Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

@@

\begin{abstract}
In this article we show an analysis of how the frequency band,
of the speckle signal, influence in the
light independence of the speckle index value in a dynamic laser speckle analysis. 
Specifically, 
will be studied as it is influenced the temporal speckle deviation 
index by the use of 3 different frequency bands of the speckle signal.
Finally, it is shown how signals with high frequency components return values with greater illumination level independence.
\end{abstract}

@@

In the ink drying test, 
we analyze the effect produced in  the speckle light intensity and, consequently, in the standard deviation index, 
by the separation of the signals in different frequency bands;
when there is a process that changes its behavior over time.

In the paper piece test, we consider that no material is completely inert, 
and consequently, 
a dynamic speckle analysis will show us how the speckle light intensity variations can be interpret as the sample activity level or as the set default level noise in the test,
we use the first case,
the effect in the speckle light intensity occasioned by the laser light intensity variation.

>>>>

\title{Study of Illumination Dependency  in the Dynamic Laser Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

@@

\begin{abstract}
In this article we show an analysis of how the frequency bands 
influence in the light independence of the speckle index value in a dynamic laser speckle analysis. 
Specifically, 
we studied temporal speckle deviation 
index influenced by the use of three different frequency bands of the speckle signal. 
Finally, it was shown how signals with high frequency components return values with greater illumination level independence.
\end{abstract}

@@

In the ink drying test, 
we analyzed the effect produced in  the speckle light intensity and, consequently, in the standard deviation index, 
by the separation of the signals in different frequency bands;
when there was a process that changes its behavior over time.

In the paper piece test, we considered that no material is completely inert, 
and consequently, 
a dynamic speckle analysis will show us how the speckle light intensity variations can be interpret as the sample activity level or as the set default level noise in the test,
we use the first case,
the effect in the speckle light intensity occasioned by the laser light intensity variation.
